Attribution of undesirable character traits, rather than trait-based dehumanization, predicts punishment decisions

### 2023-06-27 manuscript.Rmd
Did t-test calculation the other way round

hdata <- subset(Study3a_mod2,Study3a_mod2$human=='Human')
nhdata <- subset(Study3a_mod2,Study3a_mod2$human=='Non-Human')
ttest_3a1 <- t.test(hdata$values,nhdata$values,paired=TRUE)
d_3a1 <- mean(hdata$values-nhdata$values)/sd(hdata$values-nhdata$values)

@@

hdata <- subset(Study3a_mod3,Study3a_mod3$human=='Human')
nhdata <- subset(Study3a_mod3,Study3a_mod3$human=='Non-Human')
ttest_3a2 <- t.test(hdata$values,nhdata$values,paired=TRUE)
d_3a2 <- mean(hdata$values-nhdata$values)/sd(hdata$values-nhdata$values)

@@

A $2 \times 2$ within-subjects ANOVA was conducted to examine how variations in the desirability (desirable or undesirable) and humanness (uniquely human or shared with other animals) of the traits used to describe criminals influenced participants' agreement with granting them parole. In line with our prediction, a significant main effect of trait desirability was found, *F*(`r nice_3a[1,2]`) = `r nice_3a[1,4]`, *p* = `r format.pval(nice_3a[1,6], digits = 3, eps = 0.001, nsmall = 3)`, $\eta_{p}^{2}$ = `r nice_3a[1,5]`. Criminals described with socially undesirable traits (*M* = `r round(undesirable_mean, digits = 2)`, *SE* = `r round(undesirable_se, digits = 2)`) were less likely to be granted parole than were those described with desirable traits (*M* = `r round(desirable_mean, digits = 1)`, *SE* = `r round(desirable_se, digits = 2)`); see Figure \@ref(fig:figure3). A main effect of trait humanness was also found, *F*(`r nice_3a[2,2]`) = `r nice_3a[2,4]`, *p* = `r format.pval(nice_3a[2,6], digits = 3, eps = 0.001, nsmall = 3)`, $\eta_{p}^{2}$ = `r nice_3a[2,5]`. Contrary to the predictions of the dual model, however, criminals who were described with uniquely human traits (*M* = `r round(human_mean, digits = 1)`, *SE*= `r round(human_se, digits = 2)`) were less likely to be granted parole than those described with traits shared with other animals (*M* = `r round(nonhuman_mean, digits = 1)`, *SE* = `r round(nonhuman_se, digits = 2)`). A significant interaction effect between trait humanness and trait desirability was also found, *F*(`r nice_3a[3,2]`) = `r nice_3a[3,4]`, *p* = `r format.pval(nice_3a[3,6], digits = 3, eps = 0.001, nsmall = 3)`, $\eta_{p}^{2}$ = `r nice_3a[3,5]`. Criminals described using undesirable uniquely human traits (*M* = `r round(UH_undesirable_mean, digits = 1)`, *SE* = `r round(UH_undesirable_se, digits = 2)`) were less likely to be granted parole than were criminals described using desirable uniquely human traits (*M* = `r round(UH_desirable_mean, digits = 1)`, *SE* = `r round(UH_desirable_se, digits = 2)`), *t*(`r ttest_3a1$parameter`) = `r round(ttest_3a1$statistic,digits=2)`, *p* = `r format.pval(ttest_3a1$p.value, digits = 3, eps = 0.001, nsmall = 3)`, $d$ = `r round(d_3a1,digits=2)`. Similarly, criminals described using undesirable traits shared with other species (*M* = `r round(nonUH_undesirable_mean, digits = 1)`, *SE*= `r round(nonUH_undesirable_se, digits = 2)`) less likely to be granted parole than were those described using desirable traits shared with other species (*M* = `r round(nonUH_desirable_mean, digits = 1)`, *SE* = `r round(nonUH_desirable_se, digits = 2)`), *t*(`r ttest_3a2$parameter`) = `r round(ttest_3a2$statistic,digits=2)`, *p* = `r format.pval(ttest_3a2$p.value, digits = 3, eps = 0.001, nsmall = 3)`, $d$ = `r round(d_3a2,digits=2)`.

>>>>

hdata <- subset(Study3a_mod2,Study3a_mod2$human=='Human')
nhdata <- subset(Study3a_mod2,Study3a_mod2$human=='Non-Human')
ttest_3a1 <- t.test(nhdata$values,hdata$values,paired=TRUE)
d_3a1 <- mean(nhdata$values-hdata$values)/sd(nhdata$values-hdata$values)

@@

hdata <- subset(Study3a_mod3,Study3a_mod3$human=='Human')
nhdata <- subset(Study3a_mod3,Study3a_mod3$human=='Non-Human')
ttest_3a2 <- t.test(nhdata$values,hdata$values,paired=TRUE)
d_3a2 <- mean(nhdata$values-hdata$values)/sd(nhdata$values-hdata$values)

@@

A $2 \times 2$ within-subjects ANOVA was conducted to examine how variations in the desirability (desirable or undesirable) and humanness (uniquely human or shared with other animals) of the traits used to describe criminals influenced participants' agreement with granting them parole. In line with our prediction, a significant main effect of trait desirability was found, *F*(`r nice_3a[1,2]`) = `r nice_3a[1,4]`, *p* = `r format.pval(nice_3a[1,6], digits = 3, eps = 0.001, nsmall = 3)`, $\eta_{p}^{2}$ = `r nice_3a[1,5]`. Criminals described with socially undesirable traits (*M* = `r round(undesirable_mean, digits = 2)`, *SE* = `r round(undesirable_se, digits = 2)`) were less likely to be granted parole than were those described with desirable traits (*M* = `r round(desirable_mean, digits = 1)`, *SE* = `r round(desirable_se, digits = 2)`); see Figure \@ref(fig:figure3). A main effect of trait humanness was also found, *F*(`r nice_3a[2,2]`) = `r nice_3a[2,4]`, *p* = `r format.pval(nice_3a[2,6], digits = 3, eps = 0.001, nsmall = 3)`, $\eta_{p}^{2}$ = `r nice_3a[2,5]`. Contrary to the predictions of the dual model, however, criminals who were described with uniquely human traits (*M* = `r round(human_mean, digits = 1)`, *SE*= `r round(human_se, digits = 2)`) were less likely to be granted parole than those described with traits shared with other animals (*M* = `r round(nonhuman_mean, digits = 1)`, *SE* = `r round(nonhuman_se, digits = 2)`). A significant interaction effect between trait humanness and trait desirability was also found, *F*(`r nice_3a[3,2]`) = `r nice_3a[3,4]`, *p* = `r format.pval(nice_3a[3,6], digits = 3, eps = 0.001, nsmall = 3)`, $\eta_{p}^{2}$ = `r nice_3a[3,5]`. Criminals described using undesirable uniquely human traits (*M* = `r round(UH_undesirable_mean, digits = 1)`, *SE* = `r round(UH_undesirable_se, digits = 2)`) were less likely to be granted parole than were criminals described using desirable uniquely human traits (*M* = `r round(UH_desirable_mean, digits = 1)`, *SE* = `r round(UH_desirable_se, digits = 2)`), *t*(`r ttest_3a1$parameter`) = `r round(ttest_3a1$statistic,digits=2)`, *p* = `r format.pval(ttest_3a1$p.value, digits = 3, eps = 0.001, nsmall = 3)`, Cohen's $d$ = `r round(d_3a1,digits=2)`. Similarly, criminals described using undesirable traits shared with other species (*M* = `r round(nonUH_undesirable_mean, digits = 1)`, *SE*= `r round(nonUH_undesirable_se, digits = 2)`) less likely to be granted parole than were those described using desirable traits shared with other species (*M* = `r round(nonUH_desirable_mean, digits = 1)`, *SE* = `r round(nonUH_desirable_se, digits = 2)`), *t*(`r ttest_3a2$parameter`) = `r round(ttest_3a2$statistic,digits=2)`, *p* = `r format.pval(ttest_3a2$p.value, digits = 3, eps = 0.001, nsmall = 3)`, Cohen's $d$ = `r round(d_3a2,digits=2)`.

### 2023-06-27 manuscript.tex
Did t-test calculation the other way round

A \(2 \times 2\) within-subjects ANOVA was conducted to examine how variations in the desirability (desirable or undesirable) and humanness (uniquely human or shared with other animals) of the traits used to describe criminals influenced participants' agreement with granting them parole. In line with our prediction, a significant main effect of trait desirability was found, \emph{F}(1, 135) = 369.43, \emph{p} = \textless0.001, \(\eta_{p}^{2}\) = .732. Criminals described with socially undesirable traits (\emph{M} = 38.82, \emph{SE} = 1.72) were less likely to be granted parole than were those described with desirable traits (\emph{M} = 77.8, \emph{SE} = 1.44); see Figure \ref{fig:figure3}. A main effect of trait humanness was also found, \emph{F}(1, 135) = 51.62, \emph{p} = \textless0.001, \(\eta_{p}^{2}\) = .277. Contrary to the predictions of the dual model, however, criminals who were described with uniquely human traits (\emph{M} = 53, \emph{SE}= 1.36) were less likely to be granted parole than those described with traits shared with other animals (\emph{M} = 63.7, \emph{SE} = 1.5). A significant interaction effect between trait humanness and trait desirability was also found, \emph{F}(1, 135) = 54.67, \emph{p} = \textless0.001, \(\eta_{p}^{2}\) = .288. Criminals described using undesirable uniquely human traits (\emph{M} = 27.9, \emph{SE} = 1.93) were less likely to be granted parole than were criminals described using desirable uniquely human traits (\emph{M} = 78, \emph{SE} = 1.7), \emph{t}(135) = 20.75, \emph{p} = \textless0.001, \(d\) = 1.78. Similarly, criminals described using undesirable traits shared with other species (\emph{M} = 49.8, \emph{SE}= 2.32) less likely to be granted parole than were those described using desirable traits shared with other species (\emph{M} = 77.6, \emph{SE} = 1.6), \emph{t}(135) = 10.57, \emph{p} = \textless0.001, \(d\) = 0.91.

>>>>

A \(2 \times 2\) within-subjects ANOVA was conducted to examine how variations in the desirability (desirable or undesirable) and humanness (uniquely human or shared with other animals) of the traits used to describe criminals influenced participants' agreement with granting them parole. In line with our prediction, a significant main effect of trait desirability was found, \emph{F}(1, 135) = 369.43, \emph{p} = \textless0.001, \(\eta_{p}^{2}\) = .732. Criminals described with socially undesirable traits (\emph{M} = 38.82, \emph{SE} = 1.72) were less likely to be granted parole than were those described with desirable traits (\emph{M} = 77.8, \emph{SE} = 1.44); see Figure \ref{fig:figure3}. A main effect of trait humanness was also found, \emph{F}(1, 135) = 51.62, \emph{p} = \textless0.001, \(\eta_{p}^{2}\) = .277. Contrary to the predictions of the dual model, however, criminals who were described with uniquely human traits (\emph{M} = 53, \emph{SE}= 1.36) were less likely to be granted parole than those described with traits shared with other animals (\emph{M} = 63.7, \emph{SE} = 1.5). A significant interaction effect between trait humanness and trait desirability was also found, \emph{F}(1, 135) = 54.67, \emph{p} = \textless0.001, \(\eta_{p}^{2}\) = .288. Criminals described using undesirable uniquely human traits (\emph{M} = 27.9, \emph{SE} = 1.93) were less likely to be granted parole than were criminals described using desirable uniquely human traits (\emph{M} = 78, \emph{SE} = 1.7), \emph{t}(135) = -20.75, \emph{p} = \textless0.001, Cohen's \(d\) = -1.78. Similarly, criminals described using undesirable traits shared with other species (\emph{M} = 49.8, \emph{SE}= 2.32) less likely to be granted parole than were those described using desirable traits shared with other species (\emph{M} = 77.6, \emph{SE} = 1.6), \emph{t}(135) = -10.57, \emph{p} = \textless0.001, Cohen's \(d\) = -0.91.
